# Goal of this assigment

The goal of this project is to develop a shiny aplication. We are supposed to:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.

2. Deploy the application on Rstudio's shiny server

3. Share the application link by pasting it into the provided text box

4. Share your server.R and ui.R code on github

For that, I will develop a basic shiny function of a parabola, which will change as we change the chosen numbers.

## Code for the server logic of the Shiny web application

```{r}
library(shiny)
library(ggplot2)

# Function for calculating the parabola

calculateParabola <- function(x, stretchCompress, xIntercept, yIntercept) {
   y <- stretchCompress * (xIntercept - x)^2 + yIntercept
   data.frame(x=x, y=y)
}

# Define server logic required to draw a histogram

serverLogic <- function(input, output) {
   
   output$distPlot <- renderPlot({
      
      xIntercept <- input$xIntercept
      yIntercept <- input$yIntercept
      stretchCompress <- input$stretchCompress
      
      normalParabola <- calculateParabola(seq(-10,10,by=0.1),
                                          stretchCompress = 1,
                                          xIntercept = 0,
                                          yIntercept = 0)
      
      normalParabolaVertex <- calculateParabola(0,
                                          stretchCompress = 1,
                                          xIntercept = 0,
                                          yIntercept = 0)
      
      parabola <- calculateParabola(seq(-10,10,by=0.1),
                                    stretchCompress = stretchCompress,
                                    xIntercept = xIntercept,
                                    yIntercept = yIntercept)
      
      parabolaVertex <- calculateParabola(0+xIntercept,
                                  stretchCompress = stretchCompress,
                                  xIntercept = xIntercept,
                                  yIntercept = yIntercept)
      
# draw the histogram with the specified number of bins
     
       ggplot() +
         ggtitle(paste0("y = ",
                        stretchCompress, "*(", 
                        xIntercept, 
                        "-x)^2+(", 
                        yIntercept,
                        ")")) + 
         coord_cartesian(xlim = c(-10, 10), 
                         ylim = c(-10, 10)) +
         geom_line(data=normalParabola, aes(x=x, y=y), 
                   size=2, 
                   color="black", 
                   alpha=0.3) + 
         geom_vline(data=normalParabolaVertex, 
                    aes(xintercept = x), 
                    size=2
                    , 
                    color="black", 
                    alpha=0.3) +
         geom_hline(data=normalParabolaVertex, 
                    aes(yintercept=y), 
                    size=2, 
                    color="black", 
                    alpha=0.3) +
         geom_point(data=normalParabolaVertex, 
                    aes(x=x, y=y), 
                    size=6, 
                    shape = 4,
                    color="black", 
                    alpha=0.3) +
         geom_line(data=parabola, 
                   aes(x=x, y=y), 
                   size=1,
                   color="blue") + 
         geom_vline(data=parabolaVertex, 
                    aes(xintercept = x),
                    colour = "red") +
         geom_hline(data=parabolaVertex, 
                    aes(yintercept=y),
                    colour = "red") +
         geom_point(data=parabolaVertex, 
                    aes(x=x, y=y), 
                    size = 5, 
                    shape = 4,
                    colour = "red")
      
   }, height = 300, width = 300)
   
}


```
## Add serverLogic

```{r}
shinyServer(serverLogic)
```